### 2025-01-07 paper/icml25/first/figs/shacpp.tex
minors + shac/shacpp figs

        % Draw number
        \node[circle, fill=Orange,draw=Orange] (s\i) at (\sx, 0) {\color{white}$s_\i$};
        \node[circle, fill=RoyalBlue,draw=RoyalBlue] (a\i) at (\ax, -1.4) {\color{white}$a_\i$};
        \node[circle, fill=DarkOrchid,draw=DarkOrchid] (r\i) at (\ax, +1.4) {\color{white}$r_\i$};

    }
    \pgfmathsetmacro{\sx}{\nnodes*2}
    \node[circle, draw=Orange, fill=Orange] (s\nnodes) at (\sx, 0) {\color{white}$s_\nnodes$};

    % reward function
    \foreach \i in {0, ..., \nodes} {
        \pgfmathtruncatemacro{\j}{\i+1}
        \draw[-latex,line width=1,color=DarkOrchid] (a\i) -- (r\i);
        \draw[-latex,line width=1,color=DarkOrchid] (s\i) -- ($(s\i) + (.6,0)$) to[out=0,in=270]   ($(r\i) - (0,.8)$) -- (r\i);
        \draw[-latex,line width=1,color=DarkOrchid] (s\j) -- ($(s\j) - (.6,0)$) to[out=180,in=270] ($(r\i) - (0,.8)$) -- (r\i);
        \node[circle, fill=DarkOrchid,draw=white, inner sep=1.5pt] (tmp) at ($(r\i) - (0,.8)$) {};
        \node at ($(tmp) - (.25,0)$) {\color{DarkOrchid}$\hat{R}$};
    }

@@

    % value function
    \foreach \i in {1, ..., \nnodes} {
        \node[circle, fill=BlueGreen,draw=BlueGreen] (v\i) at ($(s\i) + (0,1.4)$) {\color{white}$v_\i$};
        \draw[-latex,line width=1, color=BlueGreen] (s\i) --  (v\i);
        \node[circle, fill=BlueGreen,draw=white, inner sep=1.5pt] (tmp) at ($(s\i) + (0,.6)$) {};
        \node at ($(tmp) - (.25,0)$) {\color{BlueGreen}$V_\theta$};
    }

    % transition function
    \foreach \i in {0, ..., \nodes} {
        \pgfmathtruncatemacro{\j}{\i+1}
        \draw[-latex,line width=1, color=orange] (s\i) -- (s\j) ;
        \draw[-latex,line width=1, color=orange] (a\i) -- ($(a\i) + (0,1.1)$) to[out=90,in=180] ($(s\j) - (.9,0)$) -- (s\j);
        \node[circle, fill=orange,draw=white, inner sep=1.5pt] (tmp) at ($(s\j) - (.8,0)$) {};
        \node at ($(tmp) - (0,.3)$) {\color{orange}$\hat{F}$};
    }

>>>>

        % Draw number
        \node[circle, fill=Orange,draw=Orange] (s\i) at (\sx, 0) {\color{white}$s_\i$};
        \node[circle, fill=Dandelion,draw=Dandelion, inner sep=2.2pt] (sa\i) at (\sx, 2.2) {\color{white}$s'_\i$};
        \node[circle, fill=RoyalBlue,draw=RoyalBlue] (a\i) at (\ax, -1.4) {\color{white}$a_\i$};
        \node[circle, fill=DarkOrchid,draw=DarkOrchid, inner sep=2.2pt] (r\i) at (\ax, +3.7) {\color{white}$r'_\i$};
        \node[circle, fill=DarkOrchid,draw=white,inner sep=1.5pt] (R\i) at ($(r\i) - (0,.8)$) {};
        \draw[-latex,color=DarkOrchid,line width=1] (R\i) -- (r\i);
        \node at ($(R\i) - (.3,0)$) {\color{DarkOrchid}$R_\theta$};

    }
    \pgfmathsetmacro{\sx}{\nnodes*2}
    \node[circle, draw=Orange, fill=Orange] (s\nnodes) at (\sx, 0) {\color{white}$s_\nnodes$};
    \node[circle, draw=Dandelion, fill=Dandelion, inner sep=2.2pt] (sa\nnodes) at (\sx, 2.2) {\color{white}$s'_\nnodes$};

    % reward function
    \foreach \i in {0, ..., \nodes} {
        \pgfmathtruncatemacro{\j}{\i+1}
        \draw[-,line width=1,color=DarkOrchid] (a\i) -- (R\i);
        \draw[-,line width=1,color=DarkOrchid] (sa\i) -- ($(sa\i) + (.6,0)$) to[out=0,in=270]   ($(R\i) - (0,.2)$) -- (R\i);
        \draw[-,line width=1,color=DarkOrchid] (sa\j) -- ($(sa\j) - (.6,0)$) to[out=180,in=270] ($(R\i) - (0,.2)$) -- (R\i);
    }

@@

    % value function
    \foreach \i in {1, ..., \nnodes} {
        \node[circle, fill=BlueGreen,draw=BlueGreen,inner sep=2.2pt] (v\i) at ($(sa\i) + (0,1.5)$) {\color{white}$v'_\i$};
        \draw[-latex,line width=1, color=BlueGreen] (sa\i) --  (v\i);
        \node[circle, fill=BlueGreen,draw=white, inner sep=1.5pt] (tmp) at ($(sa\i) + (0,.7)$) {};
        \node at ($(tmp) - (.25,0)$) {\color{BlueGreen}$V_\theta$};
    }

    % world model
    \draw[draw=white,fill=Dandelion,rounded corners=.5ex] ($(s0) + (-.5, 1)$) rectangle ($(s\nnodes) + (.5,1.2)$); 
    \node at ($(s0) + (-.75,1.05)$) {\color{Dandelion}$F_\theta$};
    \draw[-latex,line width=1, color=Dandelion] (s0) -- ($(s0) + (0,1)$);
    \foreach \i in {0, ..., \nodes} {
        \draw[-latex,line width=1, color=Dandelion] (a\i) -- ($(a\i) + (0,2.4)$);
    }
    \foreach \i in {0, ..., \nnodes} {
        \draw[-latex,line width=1, color=Dandelion] ($(sa\i) - (0,1)$) -- (sa\i);
    }

    % transition function
    \foreach \i in {0, ..., \nodes} {
        \pgfmathtruncatemacro{\j}{\i+1}
        \draw[-latex,line width=1, color=orange, dashed] (s\i) -- (s\j) ;
        \draw[-latex,line width=1, color=orange, dashed] (a\i) -- ($(a\i) + (0,1.1)$) to[out=90,in=180] ($(s\j) - (.9,0)$) -- (s\j);
        \node[circle, fill=orange,draw=white, inner sep=1.5pt] (tmp) at ($(s\j) - (.8,0)$) {};
        \node at ($(tmp) - (0,.3)$) {\color{orange}$\hat{F}$};
    }

### 2025-01-07 paper/icml25/first/sects/background.tex
minor on background
minors + shac/shacpp figs

To provide a context for our work, we first introduce the reinforcement learning (RL) framework and the SHAC algorithm. We model each task as a finite-horizon Markov Decision Process (MDP) $\mathcal{M} = (\mathcal{S}, \mathcal{A}, \hat{F}, \hat{R}, \gamma, T)$, where $\mathcal{S}$ is the state space, $\mathcal{A}$ is the action space, $F:\mathcal{S}\times\mathcal{A}\rightarrow\mathcal{S}$ is the transition function, $R:\mathcal{S}\times\mathcal{A}\times\mathcal{S}\rightarrow\mathbb{R}$ is the reward function, $\gamma\in\mathcal{R}$ is the discount factor, and $T\in\mathbb{N}$ is the time horizon.

The goal is to find a policy $\pi:\mathcal{S}\rightarrow\mathcal{A}$ that maximizes the expected return $J(\pi) = \mathbb{E}_{\tau\sim\pi}\left[\sum_{t=0}^{T-1}\gamma^t r(s_t, a_t, s_{t+1})\right]$, where $\tau = (s_0, a_0, s_1, a_1, \ldots)$ is a trajectory generated by the policy $\pi$.

In particular a SHAC policy is trained according the loss $\mathcal{L}_\theta^{\pi}$: 
$$ \frac{1}{NH}\sum_{i=1}^N \sum_{t=t_0}^{t_0+H-1} \gamma^{t-t_0} R(s_t^i, a_t^i) + \gamma^H V(s^i_{t_0+T})$$
Where $N$ is the number of sampled trajectories, $H << T$ is a time horizon, $s_t^i$ is the state at time $t$ of trajectory $i$, $a_t^i$ is the action at time $t$ of trajectory $i$, and $V(s):\mathcal{S}\rightarrow\mathbb{R}$ is the value function that estimates the expected return starting from state $s$. Further, SHAC assumes reward and transition functions to be differentiable, $\hat{F},\hat{R} \in \mathcal{C}^1$.

The value function is trained to approximate a temporal difference-$\lambda$ formulation \cite{Sutton98}, $\hat{V}$. In practice, the value function is trained to minimize the loss $\mathcal{L}_\theta^{V}$.

@@

$G^t_k$ represents the discounted sum of rewards up to step $k$, plus the bootstrapped value of the state at step $t+k$. The estimates $\hat{V}$ is computed by discounting more longer (higher $k$) discouunted sums, $G^k_t$.

>>>>

\subsection{Markov Decision Processes}
To provide context for our work, we first introduce the reinforcement learning (RL) framework. Each task is modeled as a finite-horizon Markov Decision Process (MDP) $\mathcal{M} = (\mathcal{S}, \mathcal{A}, \hat{F}, \hat{R}, \gamma, T)$, where $\mathcal{S}$ represents the state space, $\mathcal{A}$ denotes the action space, $\hat{F}:\mathcal{S} \times \mathcal{A} \rightarrow \mathcal{S}$ is the transition function, $\hat{R}:\mathcal{S} \times \mathcal{A} \times \mathcal{S} \rightarrow \mathbb{R}$ is the reward function, $\gamma \in [0, 1]$ is the discount factor, and $T \in \mathbb{N}$ is the time horizon.

Further, let $\mathcal{T}$ denote the space of trajectories, defined as $\mathcal{T} = (\mathcal{S} \times \mathcal{A} \times \mathcal{S} \times \mathbb{R})^*$, where each trajectory consists of a sequence of starting states, actions, subsequent states, and rewards. We will use the symbols $((s_0, a_0, s_1, r_0), (s_1, a_1, s_2, r_1), \ldots)$ to denote a trajectory in $\mathcal{T}$.

The goal of the MDP is to find a policy $\pi:\mathcal{S}\rightarrow\mathcal{A}$ that maximizes the expected return 
$$J(\pi) = \mathbb{E}_{\tau\sim\pi}\left[\sum_{t=0}^{T-1}\gamma^t r(s_t, a_t, s_{t+1})\right]$$
Where $\tau \in \mathcal{T}$ is a trajectory generated by the policy $\pi$ with the transition function $\hat{F}$.

\subsection{SHAC}

To solve an MDP $\mathcal{M} = (\mathcal{S}, \mathcal{A}, \hat{F}, \hat{R}, \gamma, T)$, SHAC trains a policy $\pi$ by minimizing the loss function $\mathcal{L}_\theta^{\pi}:\mathcal{T}^N\rightarrow\mathbb{R}$:  
$$\mathcal{L}_\theta^{\pi} = \frac{1}{NH}\sum_{i=1}^N \sum_{t=t_0}^{t_0+H-1} \gamma^{t-t_0} R(s_t^i, a_t^i) + \gamma^H V(s^i_{t_0+T}),$$  
where $N$ is the number of sampled trajectories, $H \ll T$ is a time horizon, $s_t^i$ is the state at time $t$ for trajectory $i$, $a_t^i$ is the action taken at time $t$ for trajectory $i$, and $V(s): \mathcal{S} \rightarrow \mathbb{R}$ is the value function estimating the expected return starting from state $s$. Additionally, SHAC assumes that the policy, reward, and transition functions are differentiable, i.e., $\pi, \hat{F}, \hat{R} \in \mathcal{C}^1$.

The value function is trained to approximate a temporal difference-$\lambda$ formulation \cite{Sutton98} $\hat{V}$, which in SHAC translates to minimize the loss $\mathcal{L}_\theta^{V}:\mathcal{T}^N\rightarrow\mathbb{R}$.

@@

$G^t_k$ represents the discounted sum of rewards up to step $k$, plus the bootstrapped value of the state at step $t+k$. The estimates $\hat{V}$ is computed by discounting longer (higher $k$) discounted sums, $G^k_t$.

Finally, Figure~\ref{fig:shac} presents an unrolled view of the SHAC algorithm.

### 2025-01-07 paper/icml25/first/sects/introduction.tex
minors + shac/shacpp figs

Learnign control policies has important applications in robotics~\cite{Singh22}, autonomous driving~\cite{Elallid22}, swarm intelligence~\cite{Tang21} and many other fields. 
These scenarios are varied, with can consider both single and multi-agent systems, and can have different dynamics and reward functions.
Current approaches often focus on either single- or multi-agent scenarios, lacking a unified solution that works effectively in both settings.
Moreover, reinforcement learning algorithms tend to be sample inefficient due to the high variance of the gradient estimates and the exploration required.
A recently introduced method for the latter problem is SHAC~\cite{Xu22} which exploits differentiable simulators to provide precise gradient information, thereby expediting policy optimization and improving learning efficiency.

Despite its effectiveness, the main limitations of SHAC are twofold. Firstly, it requires a differentiable simulator and differentiable reward function to work properly. Both of which may be not feasible to obtain in practice, especially with inherently sparse rewards. Secondly, even when a differentiable simulator is available, SHAC has been shown to be sensitive to complex dynamics such as object collisions~\cite{Georgiev24} or multi-agent interactions, which is currently an unsplore area in the literature.

In this work, we aim to address both these limitations by approximating the gradients of the differentiable simulator. In particular, we will replace both the simulator and the reward function with a neural network trained in tandem with the policy network and value network. Overall, this will provide an algorithm that is more robust to complex dynamics, sparse rewards, and can work in a wider range of environments, from sigle-agent to multi-agent scenarios.
On the other hand, however, this will also introduce additional complexity and computational cost tied to training additional networks.

We evaluate our framework---dubbed \fname{}---against PPO~\cite{Schulman17}, a state-of-the-art algorithm for non-differentiable environments (used also in multi-agent scenarios with the MAPPO variant~\cite{DBLP:conf/nips/YuVVGWBW22}), and SHAC~\cite{Xu22}, designed for differentiable environments. 
We compare these algorithms on VMAS---a state-of-the-art simulator for complex physics-based multi-agent scenarios~\cite{DBLP:conf/dars/BettiniKBP22}---across cooperative tasks with varying numbers of agents, enabling a systematic assessment of how their performance scales as the search space grows.

>>>>

Learnign control policies has important applications in robotics~\cite{Singh22}, autonomous driving~\cite{Elallid22}, swarm intelligence~\cite{Tang21} and many other fields. These scenarios presents a variaty of different challenges, such as sparse rewards, complex dynamics, and multi-agent interactions. Current approaches often focus on either single- or multi-agent scenarios, lacking a unified solution that works effectively in both settings. Moreover, reinforcement learning algorithms tend to be sample inefficient due to the high variance of the gradient estimates and the exploration required \texttt{\color{DarkOrchid}{<- FB: non mi è super chiara questa frase}}. A recently introduced method for the latter problem is SHAC~\cite{Xu22} which exploits differentiable simulators to provide precise gradient information, thereby expediting policy optimization and improving learning efficiency.

Despite its effectiveness, SHAC has two main limitations. First, it requires both a differentiable simulator and a differentiable reward function to operate correctly. Obtaining these can be impractical, particularly in scenarios with inherently sparse rewards. Second, even when a differentiable simulator is available, SHAC has been found to be sensitive to complex dynamics, such as object collisions~\cite{Georgiev24} or interactions in multi-agent systems.

In this work, we aim to address both limitations by approximating the gradients of the differentiable simulator. Specifically, we propose replacing both the simulator and the reward function with two neural networks trained alongside the policy and value networks. This approach is designed to create an algorithm that is more robust to complex dynamics and sparse rewards, enabling it to function effectively across a broader range of environments, including both single-agent and multi-agent scenarios. However, this method also introduces additional complexity and computational overhead due to the need for training these additional networks.

We evaluate our framework, referred to as \fname{}, against two baseline algorithms: PPO~\cite{Schulman17}, a state-of-the-art approach for non-differentiable environments (also widely used in multi-agent scenarios through the MAPPO variant~\cite{DBLP:conf/nips/YuVVGWBW22}), and SHAC~\cite{Xu22}, which is tailored for differentiable environments. The evaluation is conducted using VMAS, a state-of-the-art simulator designed for complex, physics-based multi-agent scenarios~\cite{DBLP:conf/dars/BettiniKBP22}. We compare these algorithms across cooperative tasks involving varying numbers of agents, providing a systematic analysis of how their performance scales with the increasing size of the search space.

### 2025-01-07 paper/icml25/first/sects/shacpp.tex
minors + shac/shacpp figs

@@

In practice, this is achieved by caching the state-action-reward triplets obtained from the environment and then training the neural network to minimize the MSE loss. That is, we minimize the loss $\mathcal{L}_\theta^{R}$:
$$ \frac{1}{\left|B\right|}\sum_{s,a \in B}\left|\left| R_\theta(s, a) - \hat{R}(s, a) \right|\right|^2 $$
Where $B$ represents a batch of state-action-reward triplets sampled uniformly from the cache.

Similarly, we aim to train a neural network to approximate the transition function by minimizing. However, to avoid vanishing or exploding gradients, we employ a non-recursive approach similar similar to Action World Model\cite{Ma24}. This corresponds to train a neural network that given a starting observation from $\mathcal{S}$ and a sequence of $N$ actions from $\mathcal{A}^N$, predicts the next $N$ observations from $\mathcal{S}^N$. In practice, we aim to minimize:

$$ \mathbb{E}_{\tau}\left[\sum_{i=1}^N \left|\left| F_{\theta}(s^0, a^0, \dots, a^N)^i - \hat{F}(s^i, a^i) \right|\right|^2\right] $$

Where $\tau$ corresponds to a trajectory $(s^0, a^0, s^1, a^1, \dots, s^N, a^N)$. In practice, this is achieved by caching trajectories and then training the neural network to minimize the MSE loss. That is, we minimize the loss $\mathcal{L}_\theta^{F}$:
$$ \frac{1}{\left|B\right|}\sum_{\tau \in B}\sum_{i=1}^N\left|\left| F_{\theta}(s^0, a^0, \dots, a^N)^i - \hat{F}(s^i, a^i) \right|\right|^2 $$
Where $B$ represents a batch of trajectories sampled uniformly from the cache.

While SHAC is aims to minimize $\mathcal{L}\theta^\pi$ and $\mathcal{L}_\theta^V$, we also aim to minimize also $\mathcal{L}_\theta^R$ and $\mathcal{L}_\theta^F$. Further, we modify the SHAC policy loss, $\mathcal{L}_\theta^{\pi}$, to include a term that penalizes actions outside the action space. That is, suppose the action space is $(a,b)$ (with $a<b$), we minimize the loss $\mathcal{L'}_\theta^\pi:$

@@

Where $\alpha$ is a hyper-parameter that controls the strength of the penalty. In our experiments, we set $\alpha=1$. In practice, actions are usually either clipped to the allowed action space or, an activation function is such as hyperbolic tangent is used to ensure that the actions are within the action space. This is acceptable for PPO and SHAC. However, in our scenario, this penalty is crucial. To understand why, consider that we are training the policy to optimize two neural networks that approximate the environment. Further, these networks are not trained on data generated from action inside the action space. As a result, it is very likely that these networks achieve their maximum for actions outside the allowed range. Leading to higher than normal pre-activation actions that disrupt the training process.

To summarize, our algorithm, aims to minimize the 4 presented losses, $\mathcal{L'}_\theta^{\pi}$, $\mathcal{L}_\theta^V$, $\mathcal{L}_\theta^R$, and $\mathcal{L}_\theta^F$. A minimal pseudocode of our algorithm is presented in \ref{alg:shacpp}.

However, consider that, to ensure fast convergence of the reward and transition networks, we employ a cache to store seen trajectories. To ensure that the cache is balanced, and not filled completely with $0$-reward trajectories, we divide the cache $K$ equally sized bins. Each bin is filled with trajectories that have a similar reward. For the reward network, this corresponds to the immediate reward. For the transition network, this corresponds to the sum of reward accumulated during the trajectory.

@@

    \end{algorithmic}
    \label{alg:shacpp}
    \caption{SHAC++ minimal (no cache and no cool-down) pseudocode}
\end{algorithm}

>>>>

\begin{figure*}[t]
    \centering
    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=\textwidth]{figs/shac.pdf}
        \caption{SHAC}
        \label{fig:shac}
    \end{subfigure}
    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=\textwidth]{figs/shacpp.pdf}
        \caption{\fname{}}
        \label{fig:shacpp}
    \end{subfigure}
    \caption{Comparison between SHAC and \fname{}. Nodes with labels (such as $r_i$ or $r'_i$ represents values). Nodes without labels (such as $\pi$ or $R$) represents functions. Dashed lines are used to represent non differentiability}\label{fig:shac-shacpp}
\end{figure*}

@@

In practice, this is achieved by caching the state-action-reward triplets obtained from the environment and then training the neural network to minimize the MSE loss. That is, we minimize the loss $\mathcal{L}_\theta^{R}:\mathcal{T}^N\rightarrow\mathbb{R}$:
$$ \frac{1}{\left|B\right|}\sum_{s,a,r \in B}\left|\left| R_\theta(s, a) - \underbrace{r}_{\hat{R}(s, a)} \right|\right|^2 $$
Where $B$ represents a batch of state-action-reward triplets sampled uniformly from the cache.

Similarly, we aim to train a neural network to approximate the transition function. However, to avoid vanishing or exploding gradients, we employ a non-recursive approach similar similar to Action World Model~\cite{Ma24}. This corresponds to train a neural network that given a starting observation from $\mathcal{S}$ and a sequence of $N$ actions from $\mathcal{A}^H$, predicts the next $N$ observations from $\mathcal{S}^H$. In practice, we aim to minimize:

$$ \mathbb{E}_{\tau}\left[\sum_{i=1}^H \left|\left| F_{\theta}(s_0, a_0, \dots, a_N)_i - \hat{F}(s_i, a_i) \right|\right|^2\right] $$

Where $\tau\in\mathcal{T}$. In practice, this is achieved by caching trajectories and then training the neural network to minimize the MSE loss. That is, we minimize the loss $\mathcal{L}_\theta^{F}:\mathcal{T}^N\rightarrow\mathbb{R}$:
$$ \frac{1}{NH}\sum_{\tau \in B}\sum_{i=1}^H\left|\left| F_{\theta}(s_0, a_0, \dots, a_H)_i - \underbrace{s_{i}}_{\hat{F}(s_{i-1}, a_{i-1})} \right|\right|^2 $$
Where $B$ represents a batch of trajectories sampled uniformly from the cache.

Further, we modify the SHAC policy loss, $\mathcal{L}_\theta^{\pi}$, to include a term that penalizes actions outside the action space. That is, suppose the action space is $(a,b)$ (with $a<b$), we minimize the loss $\mathcal{L'}_\theta^\pi:$

@@

    Where $\alpha$ is a hyper-parameter that controls the strength of the penalty. In our experiments, we set $\alpha=1$. Usually, actions are either clipped to the allowed action space or, an activation function (such as hyperbolic tangent or sigmoid) is used to ensure that the actions are within the allowed range. This is acceptable for PPO and SHAC. However, in our scenario, this penalty is crucial. To understand why, consider that we are training the policy to optimize two neural networks that approximate the environment. Further, these networks are never trained outside the allowed action range. As a result, it is likely that these networks will be maximized outside the allowed range thus pushing the policy to generate actions far outside the allowed range. This can ultimately result in 0-gradients when action clipping is applied or high pre-activation actions when activation function is used.

To summarize, our algorithm, aims to minimize the 4 presented losses, $\mathcal{L'}_\theta^{\pi}$, $\mathcal{L}_\theta^V$, $\mathcal{L}_\theta^R$, and $\mathcal{L}_\theta^F$. A minimal pseudocode of our algorithm is presented in \ref{alg:shacpp}. Figure~\ref{fig:shacpp} presents an unrolled view of the \fname{} algorithm.

However, consider that, to ensure fast convergence of the reward and transition networks, we employ a cache to store seen trajectories. To ensure that the cache is balanced, and not filled with $0$-reward trajectories (which are common in case of sparse rewards), we divide the cache in $K$ equally sized bins. Each bin is filled with trajectories that have a similar reward.

@@

    \end{algorithmic}
    \caption{SHAC++ minimal (no cache and no cool-down) pseudocode}
    \label{alg:shacpp}
\end{algorithm}
